---
title: "Laboratorium 3"
author: "Olaf Gontarczyk"
date: "14/06/2019"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library("nortest")
library("ggplot2")
```
#
<p><b>1. Which parameters are required to determine the normal distribution?</b></p>
  - The expectation of destribution (median and mode). And decides about the curve shifting.
  - The variance. This parameter determines the "slenderness" of the curve.
  $$N(\mu, \sigma)$$
  $$P(X \le x) = \int_{-\infty}^{+\infty} \frac{1}{\sigma\sqrt{2\pi}}e^{\frac{-(x - \mu)^2}{2\sigma^2}}$$
<p></p>

#
<p><b>2. Find another test for the normality of the distribution. What is the minimum amount of data you need for the test you have chosen?
</b></p>
<p>For the test I need more than 7 numbers</p>
```{r echo = TRUE}
data <- runif(8, 95.1, 101.5)
```

```{r echo = TRUE}
cvm.test(data)
```

```{r echo = TRUE}
ad.test(data)
```

#
<p><b>3. Generate a 300 element vector whic allow you reject the null hypotesis for the Shapiro-Wilk test</b></p>
```{r echo = TRUE}
data <- runif(300)
```
```{r echo = TRUE}
shapiro.test(data)
```
<p>$$p - value < 0.05$$</p>
<p>So, reject null hypotesis</p>
```{r echo = FALSE}
qqnorm(data)
qqline(data, col = "red")
```


#
<p><b>4. For the height of your group, verify is the average height is equal to the average height in the Poland?</b></p>
```{r echo = FALSE}
mHeight <- sample(170:207, 15)
fHeight <- sample(140:180, 10)
height <- c(mHeight, fHeight)
gender <- c(rep("m", 15), rep("f", 10))
myFrame <- data.frame(height <- height, gender <- gender)
t.test(myFrame$height, mu=180)

```
<p><i>I lost the data from the laboratory, so use random height.</i></p>

#
<p><b>5. Verify is the average height in the group differs depending on the gender?</b></p>
```{r echo = FALSE}
height <- sample(140:207, 30)
gender <- c()
for(i in height)
{
  if(i < 170)
  {
    gender = c(gender, "f")
  }
  else
  {
    gender = c(gender, "m")
  }
}
myFrame <- data.frame(height <- height, gender <- gender)
```
```{r echo = TRUE}
var_f <- with(myFrame, height[gender == "f"])
var_m <- with(myFrame, height[gender == "m"])
t.test(var_f, var_m)
```
<p><i>Yeah, a little bit.</i></p>
```{r echo = FALSE}
ggplot(myFrame, aes(x = height, fill = gender)) + geom_density()
```

